### 2018-02-28 contents/tn_sagit.tex
- sync tn-sagit changes

\section{Introduction}
\subsubsection{Trigeminal Neuralgia}
Trigeminal neuralgia (TN) is a debilitating facial neuropathic pain syndrome characterized by paroxysmal and shock-like pain in one or more divisions of the trigeminal nerve (The fifth cranial nerve, CN V) branches. TN manifests most commonly as classic (also called idiopathic TN), or secondary to a range of neuropathology, including tumors such as meningiomas \cite{Cheng2008}, trigeminal schwannomas \cite{Miller2008}, and most notably multiple-sclerosis (MS) \cite{Cruccu2009,VanderMeijs2002,Nick2012}. The pathophysiology of classic TN is thought to be vascular compression at the root of the CN V nerve entry zone (NEZ) \cite{Linn2011,Love2001}, although classic TN can also occur without evidence of vascular compression \cite{Lee2014}. While the focus of the study of TN has been primarily the peripheral segments of the trigeminal nerve, we recently compared TN and MS-TN diffusivity differences in four segments of the CN V, including at the level of the pons \cite{Chen2016a}, and confirmed that brainstem CN V diffusivity is altered in MS-TN. Similarly, we demonstrated, using multi-tensor tractography, that altered diffusivity at the level of the pons prognosticates treatment non-response \cite{Hung2017}. It appears therefore that TN is associated with unique peripheral abnormalities and brainstem related central abnormalities.

@@

\subsubsection{Acquisitions}
We studied 36 TN subjects with classic TN (28 females, 8 males; age 60.1$\pm$16.0 years; right sided pain), and 36 healthy controls (28 females, 8 males, age 42.7$\pm$12.0 years).  All TN subjects underwent non-invasive Gamma Knife radiosurgery, with imaging prior and six months post treatment. MRI acquisitions including T1 fast-spoiled gradient echo (FSPGR) and diffusion weighted image (DWI) acquisitions. 
T1 scans were acquired with 1mm slice thickness, in-plane resolution of 0.9375x0.9375 mm, with slice spacing = 1 mm, TE = 5.052 ms, TR = 11.956 ms, flip angle = $20^\circ$, FOV = 240 mm, and matrix = 256x256. 
DWI scans were acquired with 1 B0 scan, 60 gradient directions, 3 mm slice thickness and an in-plane resolution of 0.9375x0.9375 mm, where b0 = 1000 s/$mm^2$, TE = 88.6 ms, TR = 17000 ms, flip angle = $90^\circ$, field of view (FOV) = 120 mm, and matrix = 128x128.

>>>>

\section{Introduction}
\subsubsection{Trigeminal Neuralgia}
Trigeminal neuralgia (TN) is a debilitating facial neuropathic pain syndrome characterized by paroxysmal and shock-like pain in one or more divisions of the trigeminal nerve (The fifth cranial nerve, CN V) branches. TN manifests most commonly as classic (also called idiopathic TN), or secondary to a range of neuropathology, including tumors such as meningiomas \cite{Cheng2008}, trigeminal schwannomas \cite{Miller2008}, and most notably multiple-sclerosis (MS) \cite{Cruccu2009,VanderMeijs2002,Nick2012}. The pathophysiology of classic TN is thought to be vascular compression at the root of the CN V nerve entry zone (REZ) \cite{Linn2011,Love2001}, although classic TN can also occur without evidence of vascular compression \cite{Lee2014}. While the focus of the study of TN has been primarily the peripheral segments of the trigeminal nerve, we recently compared TN and MS-TN diffusivity differences in four segments of the CN V, including at the level of the pons \cite{Chen2016a}, and confirmed that brainstem CN V diffusivity is altered in MS-TN. Similarly, we demonstrated, using multi-tensor tractography, that altered diffusivity at the level of the pons prognosticates treatment non-response \cite{Hung2017}. It appears therefore that TN is associated with unique peripheral abnormalities and brainstem related central abnormalities.

@@

\subsubsection{Acquisitions}
We studied 36 TN subjects with classic TN (28 females, 8 males; age 60.1$\pm$16.0 years; right sided pain), and 36 healthy controls (28 females, 8 males, age 42.7$\pm$12.0 years).  All TN subjects underwent non-invasive Gamma Knife radiosurgery, with imaging prior and six months post treatment. MRI acquisitions including T1 fast-spoiled gradient echo (FSPGR) and diffusion weighted image (DWI) acquisitions. 
T1 scans were acquired with 1mm slice thickness, in-plane resolution of 0.9375x0.9375 mm, with slice spacing = 1 mm, TE = 5.052 ms, TR = 11.956 ms, flip angle = $20^\circ$, field of view (FOV) = 240 mm, and matrix = 256x256. 
DWI scans were acquired with 1 B0 scan, 60 gradient directions, 3 mm slice thickness and an in-plane resolution of 0.9375x0.9375 mm, where b0 = 1000 s/$mm^2$, TE = 88.6 ms, TR = 17000 ms, flip angle = $90^\circ$, FOV = 120 mm, and matrix = 128x128.
